---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.retina = 3
)

library(emoji)

manuscript_target <- targets::tar_read(manuscript)

yaml_metadata <- rmarkdown::yaml_front_matter(here::here("manuscript", "manuscript.qmd"))
title <- yaml_metadata$title
abstract <- yaml_metadata$abstract
```

# `r title`

<!-- badges: start -->
[![Preprint](https://img.shields.io/badge/Preprint-10.31235%2Fosf.io%2Fy8ked-blue)](https://doi.org/10.31235/osf.io/y8ked) [![OSF DOI](https://img.shields.io/badge/OSF-10.17605%2FOSF.IO%2FAQVNK-blue)](https://doi.org/10.17605/OSF.IO/AQVNK) [![Code DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.12817616.svg)](https://doi.org/10.5281/zenodo.12817616)
<!-- badges: end -->

[Suparna Chaudhry](https://www.suparnachaudhry.com/) • Lewis and Clark College  
[Audrey Comstock](https://audreylcomstock.weebly.com/) • Arizona State University  
[Andrew Heiss](https://www.andrewheiss.com/) • Andrew Young School of Policy Studies • Georgia State University

---

## Abstract

`r abstract`

---

## How to download and replicate

::: {.callout-note}
The complete project repository, which includes the source for [the statistical analysis notebook website](https://stats.andrewheiss.com/mountainous-mackerel/), is available at [`mountainout-mackerel`](https://github.com/andrewheiss/mountainous-mackerel) on GitHub. To replicate the findings and re-run the analysis, you can use a Docker container at [`mountainous-mackerel-docker`](https://github.com/andrewheiss/mountainous-mackerel-docker), which will create a complete computing envirionment for running everything. Full details and instructions [are available there](https://github.com/andrewheiss/mountainous-mackerel-docker).

This repository is a simplified version that only generates an HTML version of the manuscript and appendix.
:::

You can either [download the compendium as a ZIP file](/archive/main.zip) or use GitHub to clone or fork the compendium repository (see the green "Clone or download" button at the top of the GitHub page).

To maximize replicability, we wrote our manuscript using [Quarto](https://quarto.org/), which allowed us to mix computational figures, text, and tables with the actual prose of the manuscript. This means that there's no need to rely on comments within code to identify the location of each appropriate result in the manuscript—all results are programmatically included when rendering the document.

We use the [{targets} package](https://docs.ropensci.org/targets/) to manage all file dependencies and run the analysis. ([See this for a short helpful walkthrough of {targets}.](https://books.ropensci.org/targets/walkthrough.html)).

Follow these steps to install everything and replicate the results:

1. Install these preliminary things:

   - **R 4.4.0** (or later) and **RStudio**.

   - **Quarto 1.6.1** (or later). As of this writing, the current stable version of Quarto is 1.5; [download 1.6.x from GitHub](https://github.com/quarto-dev/quarto-cli/releases).

   - **A C++ compiler and GNU Make**. Complete instructions for macOS, Windows, and Linux [are available at CmdStan's documentation](https://mc-stan.org/docs/cmdstan-guide/installation.html#cpp-toolchain). In short, do this:
     - **macOS**: Run this terminal command and follow the dialog that pops up after to install macOS's Command Line Tools:

       ```sh
       xcode-select –-install
       ```

     - **Windows**: [Download and install Rtools from CRAN](https://cran.r-project.org/bin/windows/Rtools/rtools44/rtools.html)

     - **Linux**: Run this terminal command (depending on your distribution; this assumes Ubuntu/Debian):

       ```sh
       sudo apt install g++ make
       ```

   - (*macOS only*): [Download and install XQuartz](https://www.xquartz.org/)

   - **Fonts**: Download and install this font. On Windows, install is as an administrator so that R and Quarto have access to it.

     - [Noto Sans](https://fonts.google.com/specimen/Noto+Sans)

2. Open `mountainous-mackerel.Rproj` to open a new RStudio instance pointed at the project.

3. In RStudio, open `install_packages.R` and run all the code there. This uses {pacman} to install all required R packages—it downloads the latest versions of each package from CRAN and installs them systemwide.

4. Once all the package are installed, run `targets::tar_make()` in the R console to run the full analysis pipeline. This will take ≈10 minutes the first time.

   ::: {.callout-note}
   For whatever reason, when the pipeline runs it will show errors like `Error: object 'who_region' not found`. 

   These can be disregarded—everything builds fine and nothing stops with the errors—it's not clear why those are appearing ::shrug::
   :::

5. When the pipeline is all the way done, find the manuscript and appendix files at `manuscript/output/`.


## `r emoji_glue(":snow_capped_mountain::fish:")`: Note on "mountainous mackerel" project name

Because project titles change all the time with revisions, rewriting, and peer review, we used [{codename}](http://svmiller.com/codename/) to generate an [Ubuntu-style](https://wiki.ubuntu.com/DevelopmentCodeNames) internal-to-us project name that won't change.

```{r generate-code-name, eval=FALSE}
library(codename)
codename_message()
#> code name generated by {codename} v.0.4.0

codename(seed = "covid and ngos", type = "ubuntu")
#> [1] "mountainous mackerel"
```


## Licenses

**Text and figures:** All prose and images are licensed under Creative Commons ([CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)).

**Code:** All code is licensed under the [MIT License](LICENSE.md).


## Contributions and Code of Conduct

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
